---
title: "Homework 6"
author: "Saryu Patel"
date: "12/1/2021"
output: github_document
---

```{r setup, message=FALSE}
library(tidyverse)
library(modelr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%"
)
theme_set(theme_minimal())

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

### Data Cleaning

```{r}
baby_df <- 
  read_csv("data/birthweight.csv") %>%
  mutate(babysex = as.factor(babysex),
         babysex = fct_recode(babysex, "male" = "1", "female" = "2"),
         frace = as.factor(frace),
         frace = fct_recode(frace, "white" = "1", "black" = "2", "asian" = "3", 
                       "puerto rican" = "4", "other" = "8"),
         malform = as.logical(malform),
         mrace = as.factor(mrace),
         mrace = fct_recode(mrace, "white" = "1", "black" = "2", "asian" = "3", 
                       "puerto rican" = "4"))
```

There are `r sum(is.na(baby_df))` missing values.

### Propose a Model

Backward elimination will be used to determine an appropriate model, with 0.05 as the threshold.

```{r}
baby_lm1 <- lm(bwt ~ ., data = baby_df)
anova(baby_lm1)
```

`momage` has the highest p-value greater than 0.05, so it will be removed.

```{r}
baby_lm2 <- lm(bwt ~ . - momage, data = baby_df)
anova(baby_lm2)
```

`malform` has the highest p-value greater than 0.05, so it will be removed.

```{r}
baby_lm3 <- lm(bwt ~ . - momage - malform, data = baby_df)
anova(baby_lm3)
```

`menarche` has the highest p-value greater than 0.05, so it will be removed.

```{r}
baby_lm4 <- lm(bwt ~ . - momage - malform - menarche, data = baby_df)
anova(baby_lm4)
```

`ppwt` has the highest p-value greater than 0.05, so it will be removed.

```{r}
baby_lm5 <- lm(bwt ~ . - momage - malform - menarche - ppwt, data = baby_df)
anova(baby_lm5)
```

`wtgain` has the highest p-value greater than 0.05, so it will be removed.

```{r}
baby_lm6 <- lm(bwt ~ . - momage - malform - menarche - ppwt - wtgain,
               data = baby_df)
anova(baby_lm6)
```

The remaining predictors are all significant at the 0.05 level, so they will remain in the model.

The proposed model is `bwt ~ babysex + bhead + blength + delwt + fincome + frace + gaweeks + mheight + mrace + parity + ppbmi + smoken`.

### Residuals vs. Fits

```{r warning=FALSE}
baby_df %>% 
  add_predictions(baby_lm6) %>% 
  add_residuals(baby_lm6) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = 0.3) +
  labs(title = "Residuals vs. Fits")
```

### Model Comparison

```{r warning=FALSE}
set.seed(21)
cv_df <- 
  crossv_mc(baby_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble),
    my_mod = map(train, ~lm(bwt ~ . - momage - malform - menarche - ppwt - wtgain,
                              data = .x)),
    mod1 = map(train, ~lm(bwt ~ blength + gaweeks,
                          data = .x)),
    mod2 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength +
                            bhead*babysex + blength*babysex +
                            bhead*blength*babysex, 
                          data = .x)),
    rmse_my_mod = map2_dbl(my_mod, test, ~rmse(model = .x, data = .y)),
    rmse_mod1 = map2_dbl(mod1, test, ~rmse(model = .x, data = .y)),
    rmse_mod2 = map2_dbl(mod2, test, ~rmse(model = .x, data = .y))
  )
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin() +
  labs(title = "RMSE for Cross-Validated Models")
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  group_by(model) %>% 
  summarize(avg_rmse = mean(rmse)) %>% 
  knitr::kable()
```

Visually, based on the violin plot, we can see that the proposed model and model 2 have smaller RMSE than model 1. The average RMSE for the proposed model is the smallest, although model 2 comes in close second.

## Problem 2

### Import data

```{r message=FALSE}
weather_df <-  
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

### Bootstrapping

```{r}
boot_models <- 
  weather_df %>% 
  bootstrap(5000, id = "strap_number") %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
  )
```


### Estimates

#### Examine R-Squared

```{r}
r_sq <- 
  boot_models %>% 
  mutate(results = map(models, broom::glance)) %>% 
  select(strap_number, results) %>% 
  unnest(results) %>% 
  select(strap_number, r.squared)
```

Plot the distribution:

```{r}
r_sq %>% 
  ggplot(aes(x = r.squared)) +
  geom_density() +
  labs(title = "Distribution of R-Squared")
```

The mean R-squared value is about `r round(mean(r_sq$r.squared), 2)`, and it ranges from `r round(min(r_sq$r.squared), 2)` to `r round(max(r_sq$r.squared), 2)`. The distribution appears to be approximately Normal.

Confidence interval for R-squared:

```{r}
r_sq_conf <- 
  r_sq %>% 
  summarize(
    ci_lower = quantile(r.squared, 0.025),
    ci_upper = quantile(r.squared, 0.975)
  )
```

We are 95% confident that the true mean R-squared value lies between `r round(r_sq_conf$ci_lower, 2)` and `r round(r_sq_conf$ci_upper, 2)`.

#### Examine $\log(\hat{\beta}_0 * \hat{\beta}_1)$

```{r}
beta_hats <- 
  boot_models %>% 
  mutate(results = map(models, broom::tidy)) %>% 
  select(strap_number, results) %>% 
  unnest(results) %>% 
  select(strap_number, term, estimate) %>% 
  pivot_wider(names_from = term,
              values_from = estimate) %>% 
  rename(intercept = "(Intercept)") %>% 
  mutate(log_beta_hats = log(intercept * tmin))
```

Plot the distribution:

```{r}
beta_hats %>% 
  ggplot(aes(x = log_beta_hats)) +
  geom_density() +
  labs(title = "Distribution of log(B_hat_0*B_hat_1)")
```

The mean $\log(\hat{\beta}_0 * \hat{\beta}_1)$ value is about `r round(mean(beta_hats$log_beta_hats), 2)`, and it ranges from `r round(min(beta_hats$log_beta_hats), 2)` to `r round(max(beta_hats$log_beta_hats), 2)`. The distribution appears to be approximately Normal.

Confidence interval for $\log(\hat{\beta}_0 * \hat{\beta}_1)$:

```{r}
log_betas_conf <- 
  beta_hats %>% 
  summarize(
    ci_lower = quantile(log_beta_hats, 0.025),
    ci_upper = quantile(log_beta_hats, 0.975)
  )
```

We are 95% confident that the true mean $\log(\hat{\beta}_0 * \hat{\beta}_1)$ lies between `r round(log_betas_conf$ci_lower, 2)` and `r round(log_betas_conf$ci_upper, 2)`.